### 2024-09-25 manuscript.tex
Multiple additions

Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of
relatively stable and unstable conditions as determined by the LTS.  The
relatively unstable conditions are prevalent in the mid SO (50--65°S), which
might be explained by the relatively cold near-surface air overlying relatively
warm sea surface. Relatively stable conditions are prevalent elsewhere over the
SO. The distribution is also less zonally symmetric than the cyclonic activity.
In the high-latitude SO, the presence of sea ice might have significant
stabilising effect. The ERA5 renalysis is also substantially more stable than
ICON across the whole region.

@@

>>>>

Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of
relatively stable and unstable conditions as determined by the LTS.  The
relatively unstable conditions are prevalent in the mid SO (50--65°S), which
might be explained by the relatively cold near-surface air overlying relatively
warm sea surface. Relatively stable conditions are prevalent elsewhere over the
SO. The distribution is also less zonally symmetric than the cyclonic activity.
In the high-latitude SO, the presence of sea ice might have significant
stabilising effect \citep{knight2024}. The ERA5 renalysis is also substantially
more stable than ICON across the whole region.

@@

We analysed a total of about 2421 days of lidar and radiosonde data from 31
voyages and campaigns and one subantarctic station data, covering the Atlantic,
Australian and New Zealand sectors of the SO over the span of 10 years. This
dataset, together with the use of the ALCF lidar simulator, provided a fairly
comprehensive basis for evaluating SO cloud and thermodynamic profile biases in
the GSRM ICON and the ERA5 and MERRA-2 reanalyses. This provides a unique
evaluation perspective different from satellite observations, one which is
more suitable for evaluating bounary layer clouds, which are predominant in
this region. Furthermore, we subsetted our dataset by low and high latitude
bands, cyclonic activity and stability, in order to identify how these
conditions relate the the biases. Our main finding corroborates previous
findings of large boundary layer cloud biases in models, and their subsequent
effect on the radiative transfer. This also applies to the new ICON GSRM,
but the biases are lower than in the reanalyses, despite the reanalyses having
the advantage of assimilation of the observed meteorological conditions.
